Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Victor Chahuneau$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-09 paper/paper.tex
moar

% Author comments
\usepackage{color}
\usepackage{bm}
\definecolor{orange}{rgb}{1,0.5,0}
\definecolor{mdgreen}{rgb}{0,0.6,0}
\definecolor{dkblue}{rgb}{0,0,0.5}
\definecolor{dkgray}{rgb}{0.3,0.3,0.3}
\definecolor{slate}{rgb}{0.25,0.25,0.4}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{purple}{rgb}{0.7,0,1.0}
\newcommand{\ensuretext}[1]{#1}
\newcommand{\cjdmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{CJ}}_{\textsc{D}}}}}}
\newcommand{\nssmarker}{\ensuretext{\textcolor{magenta}{\ensuremath{^{\textsc{NS}}_{\textsc{S}}}}}}
\newcommand{\swmarker}{\ensuretext{\textcolor{red}{\ensuremath{^{\textsc{S}}_{\textsc{W}}}}}}
\newcommand{\ytmarker}{\ensuretext{\textcolor{blue}{\ensuremath{^{\textsc{Y}}_{\textsc{T}}}}}}
\newcommand{\ntmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{N}}_{\textsc{T}}}}}}
\newcommand{\arkcomment}[3]{\ensuretext{\textcolor{#3}{[#1 #2]}}}
%\newcommand{\arkcomment}[3]{}
\newcommand{\cjd}[1]{\arkcomment{\cjdmarker}{#1}{green}}
\newcommand{\nss}[1]{\arkcomment{\nssmarker}{#1}{magenta}}
\newcommand{\sw}[1]{\arkcomment{\swmarker}{#1}{red}}
\newcommand{\yt}[1]{\arkcomment{\ytmarker}{#1}{blue}}
\newcommand{\nt}[1]{\arkcomment{\ntmarker}{#1}{orange}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\g}{\mathbf{g}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\x}{\boldsymbol{x}}
\newcommand{\y}{\boldsymbol{y}}
\newcommand{\cost}{c}

@@

\subsection{Primary Features}
\label{sec:mainfeats}
First, we use the following four feature types as the baseline features in our
model.  For features that are sensitive to frequency, we use the log of the (frequency-plus-one) as
the feature's value.  For each feature type, we report the accuracy of using just that feature type in
isolation on the training set\cjd{training? development? cross validated?}.

\begin{compactdesc}
\item[\feat{POS}] Part-of-speech $n$-grams.  Features were extracted
  to count every POS 1-, 2-, 3- and 4-gram in each
  document. 55.18\%. \yt{CHI:IN PRP VBD, ARA:NN VBZ, KOR:DT JJ} 
\item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
  with character $n$-grams: The number of character 1-, 2-, and
  3-grams. This yielded 69.94\% accuracy.  We then refined the feature
  to include only those character $n$-grams that are observed more
  than $m$ times in the corpus are considered. $n$ ranges from~1
    to~4, and $m$ is set to~5. 74.12\% \yt{TUR:T u r k, ITA:I t a l, JPN:J a p a, \textbf{ITA: o v e} :) }  
\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
  features defined above with the prompt ID. 65.09\%.
\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown clusters 1- and 2-grams in each document. 72.26\%. \yt{in top-30 features Brown features occur up to 5 times in 10 out of 11 L1s (all except Arabic)} 
\end{compactdesc}
\noindent
The accuracy of the classifier on the development set using these four
feature types is reported in \Tref{tbl:mainfeats}.

>>>>

% Author comments
\usepackage{color}
\usepackage{bm}
\definecolor{orange}{rgb}{1,0.5,0}
\definecolor{mdgreen}{rgb}{0,0.6,0}
\definecolor{dkblue}{rgb}{0,0,0.5}
\definecolor{dkgray}{rgb}{0.3,0.3,0.3}
\definecolor{slate}{rgb}{0.25,0.25,0.4}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{purple}{rgb}{0.7,0,1.0}
\newcommand{\ensuretext}[1]{#1}
\newcommand{\cjdmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{CJ}}_{\textsc{D}}}}}}
\newcommand{\nssmarker}{\ensuretext{\textcolor{magenta}{\ensuremath{^{\textsc{NS}}_{\textsc{S}}}}}}
\newcommand{\swmarker}{\ensuretext{\textcolor{red}{\ensuremath{^{\textsc{S}}_{\textsc{W}}}}}}
\newcommand{\ytmarker}{\ensuretext{\textcolor{blue}{\ensuremath{^{\textsc{Y}}_{\textsc{T}}}}}}
\newcommand{\ntmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{N}}_{\textsc{T}}}}}}
\newcommand{\arkcomment}[3]{\ensuretext{\textcolor{#3}{[#1 #2]}}}
%\newcommand{\arkcomment}[3]{}
\newcommand{\ignore}[1]{}
\newcommand{\cjd}[1]{\arkcomment{\cjdmarker}{#1}{green}}
\newcommand{\nss}[1]{\arkcomment{\nssmarker}{#1}{magenta}}
\newcommand{\sw}[1]{\arkcomment{\swmarker}{#1}{red}}
\newcommand{\yt}[1]{\arkcomment{\ytmarker}{#1}{blue}}
\newcommand{\nt}[1]{\arkcomment{\ntmarker}{#1}{orange}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\g}{\mathbf{g}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\x}{\boldsymbol{x}}
\newcommand{\y}{\boldsymbol{y}}
\newcommand{\cost}{c}

@@

\subsection{Main Features}
\label{sec:mainfeats}
FWe use the following four feature types as the baseline features in our
model.  For features that are sensitive to frequency, we use the log of the (frequency-plus-one) as
the feature's value.  For each feature type, we report the accuracy of using just that feature type in
isolation on the training set\cjd{training? development? cross validated?} in Tab.~\ref{tbl:mainfeats}.

\begin{compactdesc}
\item[\feat{POS}] Part-of-speech $n$-grams.  Features were extracted
  to count every POS 1-, 2-, 3- and 4-gram in each
  document. 55.18\%. \ignore{CHI:IN PRP VBD, ARA:NN VBZ, KOR:DT JJ} 
\item[\feat{FreqChar}] Frequent character $n$-grams.  We experimented
  with character $n$-grams: To reduce the number of parameters, we removed features
  only those character $n$-grams that are observed more
  than $5$ times in the training corpus, and $n$ ranges from~1
    to~4. Accuracy: $74.12\%$. High-weight features include: {\tt TUR:Turk}, {\tt ITA:Ital}, {\tt JPN:Japa}.\item[\feat{CharPrompt}] Conjunction of the character $n$-gram
  features defined above with the prompt ID. Accuracy: 65.09\%.
\item[\feat{Brown}] Substitutions, deletions and insertions counts of Brown cluster unigrams and bigrams in each document. Accuracy: 72.26\%. \ignore{in top-30 features Brown features occur up to 5 times in 10 out of 11 L1s (all except Arabic)} 
\end{compactdesc}
\noindent
The accuracy of the classifier on the development set using these four
feature types is reported in \Tref{tbl:mainfeats}.
